Annotation exploration for SCPCP000006

### 2024-10-30 analyses/cell-type-wilms-tumor-06/notebook/07_annotation_Across_Samples_exploration.Rmd
Update analyses/cell-type-wilms-tumor-06/notebook/07_annotation_Across_Samples_exploration.Rmd
Co-authored-by: Stephanie Spielman <stephanie.spielman@gmail.com>

# Define normal cells
# We first pick up the immune and endothelial cells annotated via the label transfer compartments under the condition that the predicted score is above the threshold
cell_type_df$first.level_annotation[  cell_type_df$compartment %in% c("fetal_nephron", "stroma") &
                                      cell_type_df$has_cnv_score == "no CNV"]                          <- "normal"

cell_type_df$first.level_annotation[  cell_type_df$compartment %in% c("endothelium", "immune") &
                                      (cell_type_df$compartment.score > params$predicted.celltype.threshold |
                                      cell_type_df$has_cnv_score == "no CNV") ]                        <- "normal"

# Define cancer cells
cell_type_df$first.level_annotation[  cell_type_df$compartment %in% c("fetal_nephron", "stroma") &
                                      cell_type_df$has_cnv_score == "CNV" ]                            <- "cancer"

>>>>

# Define normal cells
# We first pick up the immune and endothelial cells annotated via the label transfer compartments under the condition that the predicted score is above the threshold
cell_type_df <- cell_type_df |>
  mutate(first.level_annotation = case_when(
    # assign normal/cancer based on condition
    compartment %in% c("fetal_nephron", "stroma") && has_cnv_score == "no CNV" ~ "normal",
    compartment %in% c("endothelium", "immune") && has_cnv_score == "no CNV" ~ "normal",
    compartment %in% c("fetal_nephron", "stroma") && has_cnv_score == "CNV" ~ "cancer",
    # all other cells are unknown
    .default ~ "unknown"
  ))
